\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-11-07 smurf_paper.tex
thank Mandana for help understanding the MCE xfer function

%\usepackage[pdftex,pdfpagemode={UseOutlines},bookmarks,bookmarksopen,colorlinks,linkcolor={blue},citecolor={green},urlcolor={red}]{hyperref}

%\usepackage[pdftex]{graphicx}

@@

\usepackage[bookmarks,bookmarksopen,colorlinks,linkcolor={blue},citecolor={green},urlcolor={red}]{hyperref}

@@

The James Clerk Maxwell Telescope is operated by the Joint Astronomy
Centre on behalf of the Science and Technology Facilities Council of
the United Kingdom, the Netherlands Organisation for Scientific
Research, and the National Research Council of Canada. Additional
funds for the contruction of \scuba\ were provided by the Canada
Foundation for Innovation.  This research was supported in part by the
Natural Sciences and Engineering Research Council of Canada.  EC
thanks CANARIE/CANFAR for additional funding.  The authors thank the
members of the SCUBA-2 commissioning team for testing the map-maker
and reporting anomalies; in particular Antonio Chrysostomou and Jessica
Dempsey.  We also thank Mark Halpern, Matthew
Hasselfield, and Gaelen Marsden for many useful discussions, and
observers who provided helpful feedback; especially David Nutter and
Todd McKenzie.  We acknowledge the contributions of Dennis Kelly, Alex
van Engelen and Jennifer Balfour for early investigations related to
SMURF; and Mark Thompson, Craig Walther and S\'{e}verin Gaudet for
being on the Critical Design Review panel. Finally, we thank Per
Friberg and Gary Davis for their helpful comments on the manuscript.

>>>>

\usepackage[pdftex,pdfpagemode={UseOutlines},bookmarks,bookmarksopen,colorlinks,linkcolor={blue},citecolor={green},urlcolor={red}]{hyperref}

\usepackage[pdftex]{graphicx}

@@

%\usepackage[bookmarks,bookmarksopen,colorlinks,linkcolor={blue},citecolor={green},urlcolor={red}]{hyperref}

@@

The James Clerk Maxwell Telescope is operated by the Joint Astronomy
Centre on behalf of the Science and Technology Facilities Council of
the United Kingdom, the Netherlands Organisation for Scientific
Research, and the National Research Council of Canada. Additional
funds for the contruction of \scuba\ were provided by the Canada
Foundation for Innovation.  This research was supported in part by the
Natural Sciences and Engineering Research Council of Canada.  EC
thanks CANARIE/CANFAR for additional funding.  The authors thank the
members of the SCUBA-2 commissioning team for testing the map-maker
and reporting anomalies; in particular Antonio Chrysostomou and
Jessica Dempsey.  We also thank Mark Halpern, Matthew Hasselfield, and
Gaelen Marsden for many useful discussions; observers who provided
helpful feedback, especially David Nutter and Todd McKenzie; and
Mandana Amiri for consultations regarding the SCUBA-2 Multi-Channel
Electronics.  We acknowledge the contributions of Dennis Kelly, Alex
van Engelen and Jennifer Balfour for early investigations related to
SMURF; and Mark Thompson, Craig Walther and S\'{e}verin Gaudet for
being on the Critical Design Review panel. Finally, we thank Per
Friberg and Gary Davis for their helpful comments on the manuscript.
